Reduced Gromov--Witten theory of hypersurfaces in genus one

### 2019-03-05 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
minor changes

\begin{customthm}{A}
There exists a smooth and proper Deligne—Mumford stack giving a modular compactification for the space of genus $1$ maps to projective space with fixed contact order with a hyperplane. 
\end{customthm}

With regards to the degeneration formula, we pursue the strategy laid out by Vakil and Gathmann, building on work of Caporaso and Harris. We reinterpret and extend their methods using logarithmic geometry and tropical techniques. We present a recursive scheme to calculate the invariants of a hypersurface from the invariants of projective space.

\begin{customthm}{B}
There is an explicit recursive algorithm to calculate the reduced genus one Gromov--Witten invariants of a hypersurface from that of the ambient variety. 
\end{customthm}

By standard virtual pullback techniques, virtual versions of our results apply for smooth very ample pairs $(X,Y)$.

@@

Our analysis leads naturally to a study of a ``main component’’ double ramification cycle for target manifolds in genus one. The virtual geometry of this was studied in recent work of Janda, Pandharipande, Pixton, and Zvonkine~\cite{DRCBundle}. We do not know how to calculate an expression for this main component contribution but we repurpose Maulik and Pandharipande’s rubber calculus techniques, and relations coming from the stack of target expansions, to complete our recursion. We note that even in genus one, an understanding of the main component contributions of the double ramification cycle for target manifolds would be interesting.

>>>>

\begin{customthm}{A}
There exists a log smooth and proper Deligne—Mumford stack giving a modular compactification for the space of genus $1$ maps to projective space with fixed contact order with a hyperplane. 
\end{customthm}

With regards to the degeneration formula, we pursue the strategy laid out by Vakil and Gathmann, building on work of Caporaso and Harris. We reinterpret and extend their methods using logarithmic geometry and tropical techniques. Our main result is the following.

\begin{customthm}{B}
Given a smooth pair $(X,Y)$ with $Y$ very ample, there is an explicit recursive algorithm to calculate
\begin{enumerate}
\item the reduced genus one Gromov--Witten invariants of $Y$;
\item the reduced genus one relative Gromov--Witten invariants of $(X,Y)$; 
\item the reduced genus one rubber invariants of $P=\PP_Y(\operatorname{N}_{Y|X} \oplus \OO_Y)$
\end{enumerate}
from the invariants of the ambient variety $X$.
\end{customthm}

@@

Our analysis leads naturally to a study of a ``main component’’ double ramification cycle for target manifolds in genus one. The virtual geometry of this was studied in recent work of Janda, Pandharipande, Pixton, and Zvonkine~\cite{DRCBundle}. We do not know how to calculate an expression for this main component contribution, but we repurpose E.~Katz's topological recursion relations \cite{EKatz} to complete the algorithm. We note that even in genus one, an understanding of the main component contributions of the double ramification cycle for target manifolds would be interesting.
